\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage{xcolor}
    \usepackage{hyperref}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}
\newcommand{\SEO} [1] {
    {\hspace*{-1pt}\vspace*{1pt} \textsc{#1} \textcolor{white}}
    
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Luke Alvarez}}\\
	New York $\cdot$ Lukemcp45@gmail.com $\cdot$ 1-(914)-310-3734 $\cdot$ 
\href{https://www.linkedin.com/in/luke-n-alvarez}{https://www.linkedin.com/in/luke-n-alvarez} \\
\end{center}

%==== Projects ====%
\header{Projects}
{\textbf{Personal Website }}{\sl  } \hfill \href{https://sites.google.com/view/luke-alvarez/home}{https://www.luke-alvarez.com/}\\
Personal site highlighting my accomplishments in further detail. Website built with accessibility in mind, following many WCAG guidlines, such as text descriptors for visual content.\\
\vspace*{2mm}
{\textbf{AI/ML Bees}} {\sl MLAgents,Unity,C\#, Python} \hfill
\href{https://github.com/LukeMcPartlan/MLAgentsUnityBees}{https://github.com/LukeMcPartlan/MLAgentsUnityBees}\\
A Machine Learning project thats focus was on creating different training settings to reach a 90\% success rate of a complex task in the fastest time possible.\\
\vspace*{2mm}
{\textbf{RyanRoaster}} {\sl Node.Js, JavaScript, API calls} \hfill
\href{https://github.com/LukeMcPartlan/DiscordRoastBot}{https://github.com/LukeMcPartlan/DiscordRoastBot}\\
A discord bot featuring a Node.JS backend that uses Discord API and OpenAI API calls to respond to discord messages with rude remarks about my brother!\\
\vspace*{2mm}
{\textbf{Game Engine}} {\sl Java} \hfill \href{https://www.youtube.com/watch?v=Q5191kdaQ3E}{https://www.youtube.com/watch?v=Q5191kdaQ3E}\\
A game engine and games built in it, built in college using Java Applet.\\
\vspace*{2mm}




%==== Experience ====%
\header{Work}
\vspace{1mm}

\textbf{Middletown City School District} \hfill Middletown, NY\\
\textit{Computer Science Teacher} \hfill 2020 - 2023\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Brought cutting edge CS education down to the middle school level for the first time in district.
    \item As a CS educator, I had to develop a skill set that allowed me to debug 30 bespoke student game design projects at once, requiring a deep understanding of the call stack of each project.
	\item Created and ran an Esports program. 90\% of admitted players started below the 40th percentile and finished above 80th percentile in the games\textquotesingle{} global rankings.
	\item Three interstate Esport tournament first place wins against 150+ competitors within our fist year.
	\item Established Robotics Summer camp where 7th and 8th graders went from never coding to building and coding autonomous battlebots in one week.
	\item Working with local professors and high school teachers, led the development of 8th grade CS curriculum at a one week Sienna College Computer Science Education conference; setting the standard for NYS middle school Computer Science.
	\item Led workshopping days where I helped other 8th grade technology teachers with minimal coding knowledge understand and implement the CS curriculum.
	\item Managed the schools annual technology equipment and supply budgets of \$13,000 dollars. Used this to order robot kits, 3D printers, and many other tools.
	\item Worked with architects to emphasize the tech departments needs in a \$83M renovation plan. Leveraged this to get the school an Esports room, and state of the art industrial engineering facilities.
\end{itemize}

\textbf{SUNY Orange College} \hfill Middletown, NY\\
\textit{Computer Science Adjuct Proffesor} \hfill Fall 2023\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Worked in a college setting to better understand the skill students need to excel in STEM programs.
   
\end{itemize}

\textbf{Yonkers School District} \hfill Yonkers, NY\\
\textit{Math Teacher} \hfill 2023 - 2024\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Expanded my knowlege of the STEM pipleline, teaching 7th 8th and 9th grade math sections.
    \item Had 180 percent average annual growth in 7th and 8th grade sections, as per Iready Diagnostic Testing. (80 percent higher than average growth)
   
\end{itemize}

%==== Skills ====%
\header{Skills}
\begin{tabular}{ l l }
	Programming Languages: & Java, Python, JavaScript, Block Based Languages, Solidity, LaTeX, HTML        \\
	Soft Skills:           & Leadership, Communication, Problem Solving, Continuous Learning, Collaboration \\
\end{tabular}
\vspace{2mm}

%==== Awards ====%
\header{Awards and Certificates}
\textbf{Computer Science K-12 Teaching Certification} \hfill NY State\\
One of the first to recive this cert. Official pathway opens Summer 2025 \hfill June 2023\\
\vspace*{2mm}
\textbf{Teachnology Teaching Certificate} \hfill NY State\\
Used for seated tech credits, such as industrial arts and engineering. \hfill June 2023\\
\vspace*{2mm}
\textbf{Mathmatics 7-12 Teaching Certificate} \hfill NY State\\
Core Content Certification \hfill June 2020\\
\vspace*{2mm}
\textbf{Orange and Rockland County Certificate of Excellence and Grant} \hfill Orange and Rockland County\\
Recognized for outstanding achievement in STEM education. \$1000 Grant. \hfill June 2021\\
\vspace*{2mm}
\textbf{AlgoExpert Certificate} \hfill AlgoExpert.io\\
Certification showing completion of the Algorithm Expert Curriculum. \hfill March 2023\\
\vspace*{2mm}
\textbf{BlockChain Expert Certificate} \hfill AlgoExpert.io\\
Certification showing completion of the Blockchain Expert Curriculum. \hfill April 2023\\
\vspace*{2mm}

%==== Education ====%
\header{Education}
\textbf{Lehman College}\hfill Bronx, NY\\
BS Computer Science \hfill Sep 2015 - May 2019\\
\vspace{2mm}
\textbf{Lehman College}\hfill Bronx, NY\\
Masters Mathematics Ed. \hfill Sep 2019 - May 2020\\
\vspace{2mm}
\color{white}
\tiny
SEO hidden text; things I think are cool: PyTorch , 10+ years experience being alive, certified Genius, Python, Database, SQL, FullStack, Backend, Webdev, Frontend, Git, Powershell, C, C++, Object Oriented,XML,REST,Swift,Go, JSON,Systems analysis,TypeScript,terra, ruby, ruby on rails, Kotlin, Android, Ubuntu, Linux, OS Kernal, Objective-C, Cybersecurity,Product management,Data, Database,Scrum,Agile,OOP, Django

\ 
\end{document}
